---
title: "Proposed solutions for data analyst test"
author: "Harouna TRAORE"
date: "14/02/2022"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\newpage
# Organisation of the project file

# Exercise 2: Data cleaning

For the exercise we will privilege the tidyverse environment and its set of packages.

+ Loading useful packages
```{r echo=TRUE, message=FALSE, results='hide'}
library(tidyverse) #The tidyverse environment package
library(lubridate) # For dates management
library(here) # Package for folder management
library(readxl) # for Excel dataset importation
library(infer)
```


1. Datasets importation
```{r echo=TRUE, message=FALSE, warning=FALSE, results='hide'}
# en dataset
test_data1 <- read_csv2(here::here("raw_data", "test_data_Exercise_2_en.csv"),
                      col_names=c("start","end","who","hh_ident","tg_ident","hh_sex",                      "hh_yob","sex","yob","hh_sex_b","hh_yob_b","sex_b","yob_b")
                      ,skip= 1,col_types = cols(
                        who=col_factor(levels = 
                                         c("Only target people",
                                            "Only household head",
                                              "Both household and target people")),
                      hh_ident=col_character(),tg_ident=col_character()
                      ,hh_sex=col_factor(levels = c("Female","Male")),
                      hh_yob=col_double()
                      ,sex=col_factor(levels = c("Female","Male")),
                      yob=col_double(),
                      hh_sex_b=col_factor(levels = c("Female","Male")),
                      hh_yob_b=col_double(),
                      sex_b=col_factor(levels = c("Female","Male")),
                      yob_b=col_double()
                      ))

## Dates conversion for en dataset using lubridate of tidyverse environment:
test_data1$start <- ymd_hms(test_data1$start)
test_data1$start <- ymd_hms(test_data1$start)
# alternative: test_data1$start <- as.POSIXct(test_data1$start) 
#              test_data1$end <- as.POSIXct(test_data1$end)
head(test_data1)

# xml dataset
test_data2 <- read_csv2(here::here("raw_data", "test_data_Exercise_2_xml.csv"),
                      col_types = cols(
                        who=col_factor(),
                      hh_ident=col_character(),tg_ident=col_character()
                      ,hh_sex=col_factor(levels = c("Female","Male")),
                      hh_yob=col_double()
                      ,sex=col_factor(levels = c("Female","Male")),
                      yob=col_double(),
                      hh_sex_b=col_factor(levels = c("Female","Male")),
                      hh_yob_b=col_double(),
                      sex_b=col_factor(levels = c("Female","Male")),
                      yob_b=col_double()
                      ))
## Dates conversion for xml dataset:
test_data2$start <- ymd_hms(test_data2$start)
test_data2$start <- ymd_hms(test_data2$start)

#Alternative :test_data2$start <- as.POSIXct(test_data2$start)
#             test_data2$end <- as.POSIXct(test_data2$end)
head(test_data2)

```

2. Duration, the mean and the median of a survey
```{r}

test_data1 %>%
  mutate(Survey_duration = end - start)%>%
  summarise(duration_mean=mean(Survey_duration),duration_median=median(Survey_duration))

```

3. Resolved when importing datasets but one alternative is:
```{r}
colnames(test_data1) <- names(test_data2)
head(test_data1)
```


\newpage
# Exercise 3: Data cleaning and analysis

## 1.	Data cleaning & management (20 points) 
1.1 Excel dataset importation:
```{r}
datasets <- read_excel(here::here("raw_data", "test_data_exercise_3.xlsx"))
head(datasets)
district_data <-read_excel(here::here("raw_data", "test_data_exercise_3.xlsx"),sheet="district")
head(district_data)
```
1.2 Label of the variable sex:
```{r}
labeled_sex=ifelse(datasets$sex==1,"Female","Male")
datasets <- cbind(datasets,labeled_sex)
head(datasets)
```
1.3	Renaming “country_destination” and setting negative values to missing:
```{r}
datasets <- rename(datasets,destination=country_destination)
datasets$destination<- replace(datasets$destination,which(datasets$destination < 0), NA)
head(datasets)
```
1.4 Creation of a new variable containing 5-year age brackets using the “age” variable:
```{r}


```
1.5.	Creation of a new variable containing the number of interviews that each enumerator conducted
```{r}
datasets %>%
  group_by(id)%>%
  mutate(Number_interview=sum(enumerator))

```
1.6.	Create a new variable that randomly assigns each respondent into a treatment (1) or control (0):
```{r}
set.seed(194842)
datasets$treatement <- sample(c(0,1), replace=TRUE,size=nrow(datasets))
head(datasets)
```
1.7.	Merging the population size of each district (sheet 2) to the dataset (sheet 1) so that all respondents have a corresponding value representing the population size of the district that they live in:
```{r}
merged_data <- merge(datasets, district_data, by="district")
head(merged_data)
```
1.8.Duration and mean interview time by enumerator:
```{r}
merged_data %>%
  group_by(id)%>%
  mutate(Interview_duration = endtime - starttime)%>%
  summarise(duration_mean=mean(Interview_duration))
```

1.9.	Renaming all variables in the dataset by adding the prefix “endline_” using a loop:
```{r}
# With loop:


# Alternative without loops R base:
colnames(merged_data) <- paste("Endline", colnames(merged_data), sep = "_")
head(merged_data)
```

## 2.	Data analysis & visualization 
2.1.	Creation of a summary table containing the mean age and mean number of children by district:
```{r}
merged_data %>%
  group_by(Endline_district)%>%
  summarise(mean_age=mean(Endline_age), mean_chilr=mean(Endline_children_num))
```
2.2.	Test whether the difference in age between the sexes is statistically significant at the 5% level:
```{r warning=FALSE}
merged_data %>%
   t_test(formula = Endline_age ~ Endline_sex,
      alternative = "two-sided")
```
The p_value is greater than 0.05 then we fail to reject the null hypothesis.
There is not a statistical difference between age in two groups.
